\thesistitle

### 2019-07-28 sections/clonerefactor.tex
Outline
Examples n stuff

\chapter{CloneRefactor}
% We bridged a gap between clone detection and refactoring .. by designing a tool
CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
\begin{itemize}
  \item Detection of clone classes rather than clone pairs.
  \item A novel detection method, aimed at extensibility.
  \item Detection of refactoring-oriented clone types, in addition to the literature clone types.
  \item Allows for automated refactoring of a subset of the detected duplication issues.
\end{itemize}
In this section we describe our approach and rationale for the design decisions regarding this tool.

@@

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|doA(); //{1, -2}
|\highlightYellow|doB(); //{3, -2}
doC(); //{4, -2}
doC(); //{4, -2}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doD(); //{5, -2}
|\highlightYellow|doA(); //{1, -2}
|\highlightYellow|doB(); //{3, -2}
doD(); //{5, -2}
\end{javacode}}
\colchunk[3]{
\begin{javacode}
doE(); //{6, -2}
doE(); //{6, -2}
|\highlightYellow|doA(); //{1, -2}
|\highlightYellow|doB(); //{3, -2}
\end{javacode}}
\end{parcolumns}
\caption{Cloned code fragments from figure \ref{fig:2rvariabilityhigh3} together with their equality arrays.}
\label{fig:2rvariabilityhigh4}
\end{figure}

@@

Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary. This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way.
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2) x<0 \lor y<0 \Rightarrow x=y
\end{equation}

@@

Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance. As the graph is traversed starting at the end, equal to graph traversal during clone detection, the last node in

\subsubsection{Try to Expand}
The problem with the graph clone detection technique is that ...
\todo{TODO}

>>>>

\chapter{CloneRefactor} \label{ch:clonerefactor}
% We bridged a gap between clone detection and refactoring .. by designing a tool
CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
\begin{itemize}
  \item Detection of clone classes rather than clone pairs.
  \item A novel detection method, aimed at extensibility.
  \item Detection of refactoring-oriented clone types, in addition to the literature clone types.
  \item Allows for automated refactoring of a subset of the detected duplication issues.
\end{itemize}
In this section we describe our approach and rationale for the design decisions regarding this tool.

@@

\todo{These equality arrays do not include the ( and ) separators. This is not completely right. Should we change it?}
\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|doA(); //{1, -2}
|\highlightYellow|doB(); //{3, -2}
doC(); //{4, -2}
doC(); //{4, -2}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doD(); //{5, -2}
|\highlightYellow|doA(); //{1, -2}
|\highlightYellow|doB(); //{3, -2}
doD(); //{5, -2}
\end{javacode}}
\colchunk[3]{
\begin{javacode}
doE(); //{6, -2}
doE(); //{6, -2}
|\highlightYellow|doA(); //{1, -2}
|\highlightYellow|doB(); //{3, -2}
\end{javacode}}
\end{parcolumns}
\caption{Cloned code fragments from figure \ref{fig:2rvariabilityhigh3} together with their equality arrays.}
\label{fig:2rvariabilityhigh4}
\end{figure}

@@

Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary. This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way:
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2)\text{ }x<0 \lor y<0 \Rightarrow x=y
\end{equation}

@@

Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance. The graph is traversed, starting from the last node in the code fragment (equal to graph traversal during clone detection). Because of that, $C_1$ $I_1$ is the very last clone instance in this example.

\subsubsection{Try to Expand}
The problem with the graph clone detection technique is that only single nodes that are within the variability threshold are considered duplicates of each other. However, single nodes that are not within this threshold could still be part of a clone class if the other cloned nodes are more towards the lower bound of the threshold.

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
doA(a); //{1, -2, 3, -8, -9}
|\highlightYellow|doB();
doC(a);
|\highlightYellow|doD();
|\highlightYellow|doE();
|\highlightYellow|doF();
doG(a, b, c);
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doB(d, e, f);
|\highlightYellow|doA();
|\highlightYellow|doB();
|\highlightYellow|doC();
doB(d, e, f);
\end{javacode}}
\end{parcolumns}
\caption{Type 2R clones with equality arrays and variability percentages.}
\label{fig:trytoexpand}
\end{figure}

As an example, consider the clone fragment in figure \ref{fig:trytoexpand}.

\todo{TODO}
